MaBoSS for HPC environments: Implementations of the continuous time Boolean model simulator for large CPU clusters and GPU accelerators

### 2024-04-29 Article.tex
Added first draft of MaBoSS CPU implementation

\subsubsection{MaBoSS CPU Implementation}
MaBoSS is multi-core...

>>>>

\subsubsection{MaBoSS CPU Implementation}
MaBoSS was initially developed as a single core application, but very quickly got a basic parallelism to exploit the multi-core nature of modern CPUs. In this parallel implementation the simulation of trajectories, as well as the statistics aggregation, was distributed on multiple cores (controlled by a simulation parameter) using POSIX threads. In the following sections of the papers, we will refer to this implementation as the CPU version.
